Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] correct section 4 except for last subsection

\begin{abstract}
  \todo{check}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''. There could be a bit of summary of outcome here, too}
  \todo{check captions of figures and tables}
\end{abstract}

@@

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to
\bar\mu\mu$ to derive stronger constraints than before on tensor and scalar
couplings in various model-independent scenarios and study their impact on the
not yet measured sensitive observables in $B\to K^* \bar\ell\ell$. In
\refsec{sec:EFT}, we specify the effective theory of $|\Delta B| = 1$ decays on
which our model-independent fits are based. Within this theory, we discuss the
dependence of observables in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$
on the tensor and scalar couplings in \refsec{sec:observables} and specify also
the experimental input used in the fits. The constraints on tensor and scalar
couplings from the data are presented for several model-independent scenarios in
\refsec{sec:results}.  Technical details of the angular observables in $B\to K^*
\bar\ell\ell$, the branching fraction of $B_s\to \bar\mu\mu$, the treatment of
theory uncertainties, and the Monte Carlo methods used are relegated to
appendices.

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

Eventually we also explore the effect of interference with NP in the vector
couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor and scalar
couplings.  For this purpose we include also the branching ratio, the lepton
forward-backward asymmetry, and the rate CP asymmetry of $B\to K^* \bar\mu\mu$
as they provide additional constraints on the real and imaginary parts of
$\wilson{9,\,9',\,10,\,10'}$.

The experimental inputs of all observables entering our fits is listed
in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in
$B^+ \to K^+ \bar\mu\mu$ and
their tiny SM predictions. Thus our main objective is the derivation of stronger
constraints on tensor and scalar couplings, taking advantage of their enhancement
in both observables over vector ones. For this purpose, we will consider several
model-independent scenarios, starting from rather restricted to more general ones,
in order to asses the effect of cancellations due to interference of various
contributions.

We will start with the scenario of only tensor couplings and see that they are
well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and
$B_s \to \bar\mu\mu$. Here we find that for the first time all scalar couplings
can be bounded simultaneously by the combination of both measurements. Eventually
we will consider as a special scenario the SM
augmented by dimension six operators as an effective theory of new physics below
some high scale $\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
also interference effects with new physics in vector couplings. Finally, we
conclude this section with postirior predictions of the allowed ranges of the yet
not measured angular observables in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in
$B_s\to\bar\mu\mu$ given all other experimental constraints.

\todo{Explain special initialisation of Markov chains at fixed point in parameter
space in order to avoid other local modes in subspace of nuisance parameters.
What would be appropriate place to do so?}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}

@@

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
  }
\end{table*}

In a scenario with only tensor complex-valued couplings $\wilson{T,\,
  T5}$, the experimental measurement of $F_H^\mu$ constrains the
combination $|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small
interference of $\wilson{T}$ with vector couplings
$\wilson{7,\,7',\,9,\,9'}$.  The according 68\% (95\%) 1D-marginalized
probability intervals are listed in the first column of
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in the second
column, the constraints become tighter when utilising all observables
in \reftab{tab:observables}, mainly due to the sensitivity of the
branching ratio of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see
also \reffig{fig:FHvsCT}). The latter stronger bounds are driven by
the new lattice results of $B\to K^*$ form factors that yield too high
predictions compared to the measurements~\cite{Horgan:2013pva}. Since
tensor couplings contribute constructively to ${\cal B}(B\to
K^{*}\bar\mu\mu)$ large values are stronger constrained. In this
scenario with vanishing scalar couplings, current measurements of
$A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

We also perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\,
7]$, ($i = 9,10$) in order to access the stability of the bounds
against interference. Note that $\wilson{7,7'}$ appears in linear
combinations with $\wilson{9,9'}$ such that its interference with
tensor and scalar couplings is captured implicitly by allowing new
physics in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM
value without loss of generality. In this case, $F_H^\mu$ by itself
still provides bounds on $|\wilson{T,\,T5}|$ that are weakened by a
factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional
experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in
$\wilson{9,\,10}$ become reduced and almost the same constraints on
$\wilson{T,\,T5}$ are recovered, as shown in the third column in
\reftab{tab:cTT5:1-dimCLs}.  In consequence, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the
previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by 50\%.

\fred{comment on last row: SM in all cartesian intervals but not in polar!}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{
    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
    by the black diamond.
  }
  \label{fig:scalar}
\end{figure*}

>>>>

\begin{abstract}
  \todo{check}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not-yet-measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''. There could be a bit of summary of outcome here, too}
  \todo{check captions of figures and tables}
\end{abstract}

@@

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to
\bar\mu\mu$ to derive stronger constraints than before on tensor and scalar
couplings in various model-independent scenarios and study their impact on the
not-yet-measured sensitive observables in $B\to K^* \bar\ell\ell$. In
\refsec{sec:EFT}, we specify the effective theory of $|\Delta B| = 1$ decays on
which our model-independent fits are based. Within this theory, we discuss the
dependence of observables in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$
on the tensor and scalar couplings in \refsec{sec:observables} and specify also
the experimental input used in the fits. The constraints on tensor and scalar
couplings from the data are presented for several model-independent scenarios in
\refsec{sec:results}.  Technical details of the angular observables in $B\to K^*
\bar\ell\ell$, the branching fraction of $B_s\to \bar\mu\mu$, the treatment of
theory uncertainties, and the Monte Carlo methods used are relegated to
appendices.

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{5}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    \multirow{3}{*}{${B^0\to K^{\ast 0} \bar\mu\mu}$}
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various $b\to s
  \bar\mu\mu$ decays entering the fits with the respective kinematics and
  experiments that provide the measurements. LCSR and lattice results of $B\to
  K^{(*)}$ form factors are used to constrain a $q^2$-dependent form-factor
  parametrization.  For more details see \refsec{sec:observables} and
  \refapp{app:theory:inputs}. \checked{} }
\end{center}
\end{table*}

@@

Eventually we also explore the effect of interference with NP in the vector
couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor and scalar
couplings.  For this purpose we include also the branching ratio, the lepton
forward-backward asymmetry, and the rate CP asymmetry of $B\to K^* \bar\mu\mu$
as they provide additional constraints on the real and imaginary parts of
$\wilson{9,\,9',\,10,\,10'}$. The experimental inputs of all observables
entering our fits is listed in \reftab{tab:observables} together with input for
the $B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

There are no discrepancies between the latest measurements for $\ell = \mu$
(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
main objective is to derive constraints on tensor and scalar couplings through
the enhanced sensitivity of both observables to those couplings compared to
vector couplings. For this purpose, we will consider several model-independent
scenarios, progressing from rather restricted to more general ones in order to
asses the effect of cancellations due to interference of various contributions.

For each coupling we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

We start with the scenario of only tensor couplings and see that they are well
constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
couplings can be bounded simultaneously by the combination of both
measurements. Finally we consider as a special scenario the SM augmented by
dimension six operators as an effective theory of new physics below some high
scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
electroweak symmetry breaking. In addition, the model contains one scalar
doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
interference effects with new physics in vector couplings. Finally, we conclude
this section with posterior predictions---conditional on all experimental
constraints---of the probable ranges of the not-yet-measured angular observables
in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$, $[0.03,\, 0.57]$
  & $[0.09,\, 0.33]$, $[0.02,\, 0.44]$
  & $[0.10,\, 0.33]$, $[0.02,\, 0.43]$
  \\
  \hline
  \end{tabular}

@@

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ when using
     measurements of only $F_H^\mu$, $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and finally allowing
     complex-valued new physics contributions to $\wilson{9,\,10}$. \checked{} %\fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
   }
\end{table*}

In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
values~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

We also perform a fit with non-zero $\wilson[NP]{9,\,10}$ \fred{Is this
  $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
bounds with respect to interference. Note that $\wilson{7,7'}$ appears in linear
combinations with $\wilson{9,9'}$ such that its interference with tensor and
scalar couplings is captured implicitly by allowing new physics in
$\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
generality. In this case, $F_H^\mu$ by itself still provides bounds on
$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
additional experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in $\wilson{9,\,10}$
become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%
which we attribute to cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
coordinates but never in even the 95\% region in polar coordinates. This is a
consequence of the general \emph{concentration of measure}. Another way to look
at it is to transform the uniform prior density from cartesian to polar
coordinates. For the example of the single Wilson coefficient, say $\wilson{T}$,
the transformed density is proportional to the determinant of the Jacobian which
is $|\wilson{T}|$. In words, the uniform prior on $\mbox{Re}(\wilson{T})$ and
$\mbox{Im}(\wilson{T})$ favors larger values of $|\wilson{T}|$ even though we
consider it consensus in the community that smaller rather than larger values
are held reasonable because in the SM, $\wilson{T} = 0$. We suggest therefore
that the default prior be changed in the future.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
    only $F_H^\mu$~[grey dotted, left panel], only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
    data in \reftab{tab:observables} as well as non-zero
    $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
    and 95\% (lighter) probability. The constraints on Re$(\wilson{P}Ê\pm
    \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$, apart from
    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
    indicated by the black diamond. \checked{} }
  \label{fig:scalar}
\end{figure*}

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.10,\, 0.08]$, $[-0.14,\, 0.13]$ $\quad$
  & $\quad$ $[-0.08,\, 0.07]$, $[-0.13,\, 0.13]$ $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.07,\, 0.07]$, $[-0.11,\, 0.12]$ $\quad$
  & $\quad$ $[-0.07,\, 0.07]$, $[-0.12,\, 0.11]$ $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.36,\, 0.39]$, $[-0.69,\, 0.68]$
  & $-$
  & $[-0.32,\, 0.32]$, $[-0.59,\, 0.62]$
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.37,\, 0.35]$, $[-0.68,\, 0.66]$
  & $-$
  & $[-0.25,\, 0.41]$, $[-0.57,\, 0.64]$
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[ 0.05,\, 0.20]$, $[ 0.01,\, 0.26]$
  & $[ 0.00,\, 0.16]$, $[-0.07,\, 0.22]$ \hspace{-3mm}
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.07,\, 0.08]$, $[-0.12,\, 0.12]$
  & $[-0.07,\, 0.09]$, $[-0.14,\, 0.16]$
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.24,\, 0.51]$, $[-0.51,\, 0.82]$
  & $-$
  & $[-0.12,\, 0.52]$, $[-0.42,\, 0.78]$
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.36,\, 0.37]$, $[-0.67,\, 0.67]$
  & $-$
  & $[-0.37,\, 0.29]$, $[-0.68,\, 0.57]$
  \\
  \hline
  \end{tabular}
  \end{center}

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
     at 68\% (95\%) probability from measurements of only $F_H^\mu$,
     only $\overline{\cal B}(B_s \to \bar\mu\mu)$, and all the data in
     \reftab{tab:observables} and additional new physics contributions to
     $\wilson{9,\, 9',\, 10,\,10'}$. \checked{}
   }
\end{table*}
